#Kaggle Titanic Contest

#Import required libraries
```{r}
library (tidyverse)
library (datasets)
library (visdat)
library(randomForest)
```


#Import the datafiles
```{r}
train = read.csv("C:\\Users\\hochu\\OneDrive\\Documents\\R\\Datasets\\train.csv", na.strings = "", stringsAsFactors = FALSE)

test = read.csv("C:\\Users\\hochu\\OneDrive\\Documents\\R\\Datasets\\test.csv", na.strings = "", stringsAsFactors = FALSE)
```

#Make a seperate column so we can later on distinguish the two files after we merged them
```{r}
train$Istrain = TRUE
test$Istrain = FALSE
test$Survived = NA
```


#Merge files so it's easier to clean the data
```{r}
merge = rbind(train, test)
```



#Looking at the data structures, we want to convert Survived, Pclass and Embarked to factors instead of integers

```{r}
str(merge)

merge$Pclass <- as.factor(merge$Pclass)
merge$Sex <- as.factor(merge$Sex)
merge$Embarked <- as.factor(merge$Embarked)
merge$Survived = as.factor(merge$Survived)
```


#Check to see whether it's successful
```{r}
str(merge)
```


#Check missing values in data
```{r}
merge %>%
keep(is.numeric) %>%
gather() %>%
ggplot(aes(value)) +
facet_wrap(~ key, scales = "free") +
geom_boxplot() + theme_bw()
```

```{r}
vis_dat(merge)
vis_miss(merge)
```


#Based on the graphs we can see mainly data in age is missing. The distribution of Age seems skewed because of a few outliers
```{r}
merge %>%
keep(is.numeric) %>%
gather() %>%
ggplot(aes(value)) +
facet_wrap(~ key, scales = "free") +
geom_boxplot() + theme_bw()
```


#Therefore, we replace the missing values with the median value of age.
```{r}
merge[is.na(merge$Age), "Age"] = median(merge$Age, na.rm = TRUE)
```


#Split the dataset back to train and split
```{r}
train = merge[merge$Istrain == TRUE,]
test = merge[merge$Istrain == FALSE,]
```


#Create formula with all the predictor variables
```{r}
form = as.formula("Survived ~ Age + Embarked + Pclass + Sex + Parch + Fare")
```


#Train the model
```{r}
rf_model = randomForest(formula = form, data = train, ntree = 500, mty = 6)
```



#Now that we trained our model, we test it on the test set
```{r}
Survived = predict(rf_model, newdata=test)
```

#Check prediction
Survived

#Now we save our output in the requested file format
```{r}
PassengerId = test$PassengerId

df = as.data.frame(PassengerId)

df$Survived = Survived

write.csv(df, file="baseSubmission.csv", row.names = FALSE)

str(df)
```


